Multiproduct Batch Processing Time Maximization Problem

### 2023-06-17 (2023) Fraga et al.tex
updating paper
correction in min math function presentation

\begin{equation}
T' = \min {\textrm{UD}_i / \textrm{p}_i}
\end{equation}

@@

\begin{equation}
T'' = \min \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i, (\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}
\end{equation}

@@

\begin{equation}
T = \min {T , Z}
\end{equation}

@@

Note that it is not important to know the values of $O_i$ and $I_i$ however these values can be found by solving the indeterminate system of equations:

>>>>

\begin{equation}
T' = \min_{\forall i} \{\textrm{UD}_i / \textrm{p}_i\}
\end{equation}

@@

\begin{equation}
T'' = \min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}
\end{equation}

@@

\begin{equation}
T = \min \{T , Z\}
\end{equation}

@@

Note that it is not important to know the values of $O_i$ and $I_i$ $\forall i$ however these values can be found by taking a solution from the indeterminate system of inequations:
